SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-09 SI.tex
Update

\title{SUPPLEMENTARY INFORMATION: NMRlipids Databank makes data-driven analysis of biomembrane properties accessible for all}

@@

\begin{table}[!h]
    \centering
    %\begin{tabular}{c c c c}
    \begin{tabular}{p{3.0cm}  p{5.0cm}  p{3.0cm}  p{4.0cm}}
        Code & Function & Input & Output \\
        \hline
        \multicolumn{4}{c}{ {\bf Databank layer}}\\
        \hline
        \multicolumn{4}{c}{ {\bf Scripts/BuildDatabank/ }}\\
         AddData.py & Create README.yaml from user given information in info.yaml  & info.yaml & README.yaml \\
         searchDATABANK.py & Pair simulations with available experimental data  & README.yaml files & Updated README.yaml files \\
         QualityEvaluation.py & Quality-evaluate simulations that are paired with experimental data  & README.yaml files & [lipid\_name]\_OrderParameters\_quality.json, [lipid\_name]\_FragmentQuality.json, system\_quality.json, FormFactorQuality.json \\
         \multicolumn{4}{c}{ {\bf Scripts/AnalyzeDatabank/ }}\\
         calcOrderParameters.py & Calculate C-H bond order parameters for all lipids in the simulation & README.yaml files & [lipid\_name]\_OrderParameters.json \\
         calcAPL.py & Calculate area per lipid as a function of time & README.yaml files & apl.json \\
         calc\_FormFactors.py & Calculate x-ray scattering form factors & README.yaml files & FormFactor.json \\
         calc\_thickness.py & Calculate membrane thickness & README.yaml files & thickness.json \\
         template.py $\qquad$  template.ipynb & Minimal code to loop over simulations that can be used as a template for new analyses & README.yaml files & \\

@@

\begin{table}[p]
    \centering
    \begin{tabular}{c c}
    Abbreviation & Molecule name \\
    \hline
    Lipids and surfactants & \\
    \hline
    POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
    POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
    POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
    POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
    PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
    PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
    DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
    DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
    DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
    DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
    DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
    DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
    DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
    DOG  & 1,2-dioleoyl-sn-glycerol \\
    DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
    DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
    DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
    DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
    DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
    DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
    SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
    DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
    SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
    POPI & \\ 
    SAPI & \\
    SLPI &  \\
    SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
    SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
    CER  & N-palmitoyl-D-erythro-sphingosine \\
    CHOL & cholesterol  \\
    DCHOL & 18,19-di-nor-cholesterol \\
    DHMDMAB & dihexadecyldimethylammonium  \\
    \hline
    Other molecules & \\
    \hline
    POT & potassium ion  \\
    SOD & sodium ion  \\
    CLA & chloride ion \\
    CAL & calcium ion  \\
    CES & caesium ion \\
    SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecule names used in the Databank.}
    \label{tab:abbreviations}
\end{table}

>>>>

\title{SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all}

@@

\begin{table}[!h]
    \centering
    %\begin{tabular}{c c c c}
    \begin{tabular}{p{3.0cm}  p{5.0cm}  p{3.0cm}  p{4.0cm}}
        Code & Function & Input & Output \\
        \hline
        \multicolumn{4}{c}{ {\bf Databank layer}}\\
        \hline
        \multicolumn{4}{c}{ {\bf Scripts/BuildDatabank/ }}\\
         AddData.py & Create README.yaml from user given information in info.yaml  & info.yaml & README.yaml \\
         searchDATABANK.py & Pair simulations with available experimental data  & README.yaml files & Updated README.yaml files \\
         QualityEvaluation.py & Quality-evaluate simulations that are paired with experimental data  & README.yaml files & [lipid\_name]\_OrderParameters\_quality.json, [lipid\_name]\_FragmentQuality.json, system\_quality.json, FormFactorQuality.json \\
         \multicolumn{4}{c}{ {\bf Scripts/AnalyzeDatabank/ }}\\
         calcOrderParameters.py & Calculate C-H bond order parameters for all lipids in the simulation & README.yaml files & [lipid\_name]\_OrderParameters.json \\
         calcAPL.py & Calculate area per lipid as a function of time & README.yaml files & apl.json \\
         calc\_FormFactors.py & Calculate x-ray scattering form factors & README.yaml files & FormFactor.json \\
         calc\_thickness.py & Calculate membrane thickness & README.yaml files & thickness.json \\
         %template.py $\qquad$  template.ipynb & Minimal code to loop over simulations that can be used as a template for new analyses & README.yaml files & \\

@@

\begin{comment}

\begin{table}[p]
    \centering
    \begin{tabular}{c c}
    Abbreviation & Molecule name \\
    \hline
    Lipids and surfactants & \\
    \hline
    POPC &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphocholine  \\
    POPG &  1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoglycerol \\
    POPS & 1-palmitoyl-2-oleoyl-sn-glycero-3-phospho-L-serine \\
    POPE & 1-palmitoyl-2-oleoyl-sn-glycero-3-phosphoethanolamine \\
    PYPC & 1-(16:0)-2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    PAzePCprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine protonated \\
    PAzePCdeprot & 1-palmitoyl-2-azelaoyl-sn-glycero-3-phosphocholine deprotonated \\
    DMPC & 1,2-dimyristoyl-sn-glycero-3-phosphocholine \\
    DPPC & 1,2-dipalmitoyl-sn-glycero-3-phosphocholine \\
    DPPE & 1,2-dipalmitoyl-sn-glycero-3-phosphoethanolamine \\
    DPPG & 1,2-dipalmitoyl-sn-glycero-3-phospho-(1'-rac-glycerol) (sodium salt) \\
    DEPC & 1,2-dierucoyl-sn-glycero-3-phosphocholine \\
    DRPC & 1,2-(14:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DYPC & 1,2-(16:1$^\Delta9$)-sn-glycero-3-phosphocholine \\
    DLPC & 1,2-dilauroyl-sn-glycero-3-phosphocholine \\
    DLIPC& 1,2-dilinoleoyl-sn-glycero-3-phosphocholine \\
    DOG  & 1,2-dioleoyl-sn-glycerol \\
    DOPC & 1,2-dioleoyl-sn-glycero-3-phosphocholine \\
    DOPE & 1,2-dioleoyl-sn-glycero-3-phosphoethanolamine \\
    DDOPC& 1,2-didocosahexaenoyl-sn-glycero-3-phosphocholine \\
    DOPS & 1,2-dioleoyl-sn-glycero-3-phospho-L-serine \\
    DSPC & 1,2-distearoyl-sn-glycero-3-phosphocholine \\
    DAPC & 1,2-diarachidonoyl-sn-glycero-3-phosphocholine \\
    SLiPC & 1-(18:0)-2-(18:2 $^{\Delta9,12}$)-sn-glycero-3-phosphocholine  \\
    DMTAP & 1,2-dimyristoyl-3-trimethylammonium-propane \\
    SOPC & 1-stearoyl-2-oleoyl-sn-glycero-3-phosphocholine \\
    POPI & \\ 
    SAPI & \\
    SLPI &  \\
    SDG & 1-stearoyl-2-docosahexaenoyl-sn-glycerol \\
    SDPE & 1-stearoyl-2-docosahexaenoyl-sn-glycero-3-phosphoethanolamine \\
    CER  & N-palmitoyl-D-erythro-sphingosine \\
    CHOL & cholesterol  \\
    DCHOL & 18,19-di-nor-cholesterol \\
    DHMDMAB & dihexadecyldimethylammonium  \\
    \hline
    Other molecules & \\
    \hline
    POT & potassium ion  \\
    SOD & sodium ion  \\
    CLA & chloride ion \\
    CAL & calcium ion  \\
    CES & caesium ion \\
    SOL & water  \\
    \end{tabular}
    \caption{Abbreviations for molecule names used in the Databank.}
    \label{tab:abbreviations}
\end{table}
\end{comment}
